Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-20 papers/BON_VHDL/paper.tex
more text
text

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation 
for object-oriented systems  which emphasizes \emph{seamlessness}, 
\emph{reversibility} and software \emph{contracting}. Let us define 
these principles precisely and point out why the principles are 
important in VHDL-AMS simulation.
%\todo{dragan 25/07/2009 - Figure out relation: Seamlessness and VHDL-AMS}
\begin{itemize}
\item \emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
%\todo{dragan 25/07/2009 - Figure out relation: Reversibility and VHDL-AMS. Why is Reversibility important in VHDL design.}
\item \emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design while bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code.
\item \emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, simulator evaluates quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We admit that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which the summation
of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any closed path (loop) equals zero and the summation of
through quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node (point) equals zero.
Finally, any predefined (implicite) attribute in VHDL has defined \emph{pre(post)condition} trought
input/output parameters constraints.

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.  
\section{Mapping between BON and VHDL-AMS}

\section{Refinement from BON to VHDL-AMS}

@@

>>>>

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation 
for object-oriented systems  which emphasizes \emph{seamlessness}, 
\emph{reversibility} and software \emph{contracting}. Let us define 
these principles precisely and point out why the principles are 
important in VHDL-AMS simulation.
%\todo{dragan 25/07/2009 - Figure out relation: Seamlessness and VHDL-AMS}
\begin{itemize}
\item \emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
%\todo{dragan 25/07/2009 - Figure out relation: Reversibility and VHDL-AMS. Why is Reversibility important in VHDL design.}
\item \emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design while bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code.
\item \emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, simulator evaluates quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We admit that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which the summation
of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any closed path (loop) equals zero and the summation of
through quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node (point) equals zero.
Finally, any predefined (implicite) attribute in VHDL has defined \emph{pre}/\emph{(post)condition} trought
input/output parameters and theirs constraints.

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.

\section{Refinement from VHDL-AMS to BON }

@@

\section{Mapping between BON and VHDL-AMS}
